Declarative Deployment Reconfiguration of Pulverised Collective Adaptive Systems at Runtime \thanks{ This work has been supported by the Italian PRIN Project COMMON-WEARS (2020HCWWLP) and the EU/MUR FSE REACT-EU PON R\&I 2014-2020. }

### 2023-05-21 paper-2023-acsos-pulverization.tex
typos, punctuations, language, conciseness, clarity

Although the idea behind pulverisation is simple,
finding a way to implement it effectively requires tackling several challenges at different levels:
\begin{itemize}
    \item \textbf{communication}: splitting logical devices into small deployment units implies communication among them,
    thus requiring to consider networking at two levels:
    across pulverised components (intra-device) and among logical devices (inter-device);
    \item \textbf{portability}: hosts will have very diverse hardware specifications, operating systems, and software stacks;
    \item \textbf{runtime}: the system should be able to reconfigure its deployment at runtime without disrupting the application logic; and
    \item \textbf{language}: for the idea to be exploitable by designers it is important that
    the pulverised configuration
    and the mapping of pulverised components to the underlying infrastructure
    can be expressed easily and, possibly, declaratively.
\end{itemize}

>>>>

Although the idea behind pulverisation is simple,
finding a way to implement it effectively requires tackling several challenges at different levels:
\begin{itemize}
    \item \textbf{communication}: splitting logical devices into small deployment units implies communication among them,
    thus requiring to consider networking at two levels:
    across pulverised components (intra-device) and among logical devices (inter-device);
    \item \textbf{portability}: hosts will have very diverse hardware specifications, operating systems, and software stacks;
    \item \textbf{runtime}: the system should be able to reconfigure its deployment at runtime without disrupting the application logic; and
    \item \textbf{language}: for the idea to be exploitable by designers,
    it is essential that
    the pulverised configuration
    and the mapping of pulverised components to the underlying infrastructure
    can be expressed easily and, possibly, declaratively.
\end{itemize}
